discussion

### 2018-09-18 man/ms_3_discussion.Rmd
update discussion

Our results showed differences for greenness and tree-growth between northern and southern oak populations (Table 3). Las poblaciones del norte, que presentan condiciones mas secas (Tabla 1), se vieron mas afectadas por los eventos de sequía. Por ejemplo las anomalías estandarizadas de EVI fueron mas negativas (mayor intensidad en el browning) en la población del norte durante la sequía de 2005. SJ site showed stronger correlations of tree-growth with SPEI (Hydrological and summer) (Figure 6), which can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014].

@@

A striking result is the difference for tree growth between sites (Figure 4). The trees of CA-High site, which are located around 1900 m. a.s.l. and representing the upper limit of the treeline of the species in this southernmost location, showed higher BAI than those located at low-elevations sites (CA-Low and SJ) (Figure 4). This is especially interesting for southern sites, which are very close to each other. Our results are consistent with previous findings that pointed out tree growth and tree responses to drought are site-dependent (e.g. soil features, tree competence, etc.) [e.g. @Babst2013; @VicenteSerrano2014b], particularly for rear-edge populations [@Cavin2017; @Dorado2017c].

@@

@@

Another reason that could explain the higher values of BAI of CA-High site is el grado diferente de impacto antrópico. En nuestros resultados vemos como los bosques situados a mayor altitud presentan un menor impacto antrópico. Esto puede ser simplemente por el hecho de que estos bosques estén menos accesibles ---> ojo y la idea de que son bosque relativamente jóvenes 
---> Gráfica 
Our sampled sited showed similar tree competence levels (Table 1), but ... impacto antrópico diferente

@@

Tanto en el greenness como en el growth, encotramos direfencias para el greenness y el crecimiento entre las poblaciones situadas al norte y al sur.

Esta tendencia es importante sobre todo en las poblaciones situadas mas al sur, en donde observamos: menor br
Encontramos diferencias entre poblaciones. Asi por ejemplo en las situadas mas al sur, vemos que las anomalias de EVI son menos negativas para el 2005; También vemos tendencias positivas en el BAI...

@@

#### Climate and tree relationship

Frase de resultados que tenemos que poner en discussion: 
Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth (Figure 7b), specially for the northern population (r > 0.6), ... **which can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014]**.

@@

duda --> las proyecciones de crecimiento que hiciste [@GeaIzquierdo2013] sugerían un declive en el crecimiento. Nosotros estamos obteniendo algo diferente no? DUDA

>>>>

Our results showed differences for greenness and tree-growth between northern and southern oak populations (Table 3). Las poblaciones del norte, que presentan condiciones mas secas (Tabla 1), se vieron mas afectadas por los eventos de sequía. For instance, the northern site showed more negative EVI standardized anomalies (higher browning intensity) than the southern sites during the 2005 drought event (Figure 2). In addition, the stronger correlations of tree-growth with SPEI (Hydrological and summer) observed for SJ site (Figure 6), can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014].

@@

A striking result is the difference for tree growth between sites (Figure 4). The trees of CA-High site, which are located around 1900 m. a.s.l. and representing the upper limit of the treeline of the species in this southernmost location [@PerezLuque2011tfm], showed higher BAI than those located at low-elevations sites (CA-Low and SJ) (Figure 4). This is especially interesting for southern sites, which are very close to each other. Our results are consistent with previous findings that pointed out tree growth and tree responses to drought are site-dependent (e.g. soil features, tree competence, etc.) [e.g. @Babst2013; @VicenteSerrano2014b], particularly for rear-edge populations [@Cavin2017; @Dorado2017c].

@@

***Reescribir esto del impacto antrópico***

@@

Another reason that could explain the higher values of BAI of CA-High site is el grado diferente de impacto antrópico. En nuestros resultados vemos como los bosques situados a mayor altitud presentan un menor impacto antrópico. Esto puede ser simplemente por el hecho de que estos bosques estén menos accesibles ---> ojo y la idea de que son bosque relativamente jóvenes

* ---> Gráfica. Our sampled sited showed similar tree competence levels (Table 1), but ... impacto antrópico diferente

@@

@@

```{r echo=FALSE, results='asis', eval=show_text}
cat("
#### Climate and tree relationship

Frase de resultados que tenemos que poner en discussion: 
Precipitation of previous december was also positively correlated with tree growth in the northern population and in the highest location of the southern population. Hydrological, Spring and Summer SPEI showed a strong positive correlation with tree-growth (Figure 7b), specially for the northern population (r > 0.6), ... **which can be interpreted as higher sensitivity to drought of a drier site [@GeaIzquierdo2014]**.  
")
```

@@
